Learning and comparing functional connectomes between populations

### 2012-12-25 paper.tex
Redo figures

%{{{------ Regressor in precision matrix -------------------------------------
\begin{figure}
\includegraphics[width=.495\linewidth]{group_l21_prec_no_confounds.pdf}%
\hspace*{1pt}%
\includegraphics[width=.495\linewidth]{group_l21_prec_global_mean.pdf}%

@@

For the problem of recovering the functional-connectivity
\emph{structure}, \emph{i.e.}\ finding which region is connected to
which, sparse inverse covariance estimators have been found to be
efficient \cite{varoquaux2010c, smith2011}. The intuition for relying on
inverse covariance rather than correlation stems from that fact that
standard correlation (marginal correlation) between two variables $a$ and
$b$ also capture the effects of other variables -- strong correlation of
$a$ and $b$ with a third variable $c$ will induce a correlation between
$a$ and $b$. On the opposite, the inverse covariance\footnote{Covariance
and correlation matrices differ simply by the fact that a covariance
matrix captures the amplitude of a signal, via its variance, while a
correlation matrix is computed on normalized signals.}
matrix captures
partial correlations, removing the effect of other variables
\cite{marrelec2006a}. In the small sample limit, this removal is
challenging from the statistical standpoint, and assumption of sparsity,
\emph{i.e.}\ that only few variables need to be considered at a time, is
important to estimate a good inverse covariance. Various estimation
strategies exist for sparse inverse covariance, and have an impact on the
resulting networks \cite{varoquaux2012,varoquaux2010c}. The
graphical-lasso ($\ell_1$-penalized maximum-likelihood estimator)
\cite{friedman2008} is a good general-purpose approach. In group studies,
the $\ell_{21}$ estimator \cite{varoquaux2010c,honorio2012} is useful to
impose a common sparsity structure across different subjects and achieve
better recovery of this common structure. Simply put, these approaches
are necessary because estimation noise creates a background structure
(see Fig\,\ref{fig:icov}); however, unlike in a univariate situation, the
parameters are not independent, and the spurious background connections
degrade the estimation of the actual connections. The sparse estimators
make a compromise between imposing simpler models, \emph{i.e.}\ with less
connections, and fitting well the data. This compromise is set via a
regularization parameter which controls the sparsity of the estimate. A
good rule of thumb to set this parameter is via cross-validation
\cite{varoquaux2010c}.

>>>>

%{{{------ Regressor in precision matrix -------------------------------------
\begin{figure}
\includegraphics[height=.482\linewidth]{group_l21_prec_no_confounds.pdf}%
\hspace*{1pt}%
\includegraphics[height=.482\linewidth]{group_l21_prec_global_mean.pdf}%
\hspace*{1pt}%
\includegraphics[height=.482\linewidth]{cmap.pdf}%

@@

For the problem of recovering the functional-connectivity
\emph{structure}, \emph{i.e.}\ finding which region is connected to
which, sparse inverse covariance estimators have been found to be
efficient \cite{varoquaux2010c, smith2011}. The intuition for relying on
inverse covariance rather than correlation stems from that fact that
standard correlation (marginal correlation) between two variables $a$ and
$b$ also capture the effects of other variables -- strong correlation of
$a$ and $b$ with a third variable $c$ will induce a correlation between
$a$ and $b$. On the opposite, the inverse covariance\footnote{Covariance
and correlation matrices differ simply by the fact that a covariance
matrix captures the amplitude of a signal, via its variance, while a
correlation matrix is computed on normalized signals.}
matrix captures
partial correlations, removing the effect of other variables
\cite{marrelec2006a}. In the small sample limit, this removal is
challenging from the statistical standpoint, and assumption of sparsity,
\emph{i.e.}\ that only few variables need to be considered at a time, is
important to estimate a good inverse covariance. Various estimation
strategies exist for sparse inverse covariance, and have an impact on the
resulting networks \cite{varoquaux2012,varoquaux2010c}. The
Graph Lasso ($\ell_1$-penalized maximum-likelihood estimator)
\cite{friedman2008} is a good general-purpose approach. In group studies,
the $\ell_{21}$ estimator \cite{varoquaux2010c,honorio2012} is useful to
impose a common sparsity structure across different subjects and achieve
better recovery of this common structure. Simply put, these approaches
are necessary because estimation noise creates a background structure
(see Fig.\,\ref{fig:icov_estimators}); however, unlike in a univariate situation, the
parameters are not independent, and the spurious background connections
degrade the estimation of the actual connections. The sparse estimators
make a compromise between imposing simpler models, \emph{i.e.}\ with less
connections, and fitting well the data. This compromise is set via a
regularization parameter which controls the sparsity of the estimate. A
good rule of thumb to set this parameter is via cross-validation
\cite{varoquaux2010c}.
